A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-10 sections/Metatheory.tex
a few edits in section 4

This section presents the metatheory of the algorithmic system
presented in Section~\ref{}. We show that three main results hold: 
\emph{soundness}, \emph{completeness} and \emph{decidability}.
All the results have been mechanically formalized and proved in the 
Abella theorem prover.

@@

The transfer rules are shown in Figure~\ref{fig:trans}.
Rule $\mathtt{{\sto}\al}$ recursively replaces the first existential variable to a well-scoped monotype.
Note that $\Om$, as a declarative worklist, contains no existential
variables. Therefore by recursively applying this rule, the
algorithmic worklist will finally become a declarative one.
In order to maintain well-formedness,
the substitution should affect all the judgments and term variable bindings in the scope of $\al$.

>>>>

This section presents the metatheory of the algorithmic system
presented in the previous section. We show that three main results hold: 
\emph{soundness}, \emph{completeness} and \emph{decidability}.
These three results have been mechanically formalized and proved in the 
Abella theorem prover~\cite{}.

@@

The transfer rules are shown in Figure~\ref{fig:trans}.
Rule $\mathtt{{\sto}\al}$ replaces the first existential variable with a well-scoped monotype and
repeats the process in the resulting worklist.
Note that $\Om$, as a declarative worklist, contains no existential
variables. Therefore by recursively applying this rule, the
algorithmic worklist will finally become a declarative one.
In order to maintain well-formedness,
the substitution should affect all the judgments and term variable bindings in the scope of $\al$.
